Assessment of zonal symmetric and asymmetric components of the Southern Annular Mode using a novel approach

### 2020-12-11 analysis/paper/paper.tex
Declaraciones

\hypertarget{data-statement}{%
\subsection{Data statement}\label{data-statement}}

@@

>>>>

\hypertarget{declarations}{%
\section*{Declarations}\label{declarations}}
\addcontentsline{toc}{section}{Declarations}

\hypertarget{funding}{%
\subsection*{Funding}\label{funding}}
\addcontentsline{toc}{subsection}{Funding}

The research was supported by UBACyT20020170100428BA and the CLIMAX Project funded by Belmont Forum/ANR-15-JCL/-0002-01. Elio Campitelli was supported by a PhD grant from CONICET, Argentina.

\hypertarget{conflicts-of-interest}{%
\subsection*{Conflicts of interest}\label{conflicts-of-interest}}
\addcontentsline{toc}{subsection}{Conflicts of interest}

The authors declare that they have no conflict of interest.

\hypertarget{availability-of-data-and-material}{%
\subsection*{Availability of data and material}\label{availability-of-data-and-material}}
\addcontentsline{toc}{subsection}{Availability of data and material}

@@

\hypertarget{code-availability}{%
\subsection*{Code availability}\label{code-availability}}
\addcontentsline{toc}{subsection}{Code availability}
